On the presentation of orthogonal groups over polynomial rings

### 2019-01-07 dl-paper.tex
Fixed notation for symbols

Statement \[x_{\alpha}(aX^{-1}) g x_{\alpha}(-a(1+am)^{-1}X^{-1}) \cdot \{X, 1+am\} \in G_+.\]

$g = x_{-\alpha}(mX)$,

$y := x_{\alpha}(aX^{-1}) g x_{\alpha}(-a(1+am)^{-1}X^{-1})$,

@@

$\alpha = h_{ik}^{-1}(X)$.

Using $\pi(z) = 1$ we get 
\begin{multline}z = z^\alpha = \\ x_{ji}(-m(1+am)^{-1}) x_{ij}(a) x_{ji}(m) \cdot x_{ij}(-a(1+am)^{-1})\{X, (1+am)^{-1}\} \cdot h_{ij}((1+am)^{-1}) \in G. \end{multline}

>>>>

$\langle \alpha, \beta \rangle = (\alpha, \beta^\vee) = (\alpha, \frac{2\beta}{(\beta, \beta)})$
Our convention for Cartan matrices is 
$A_{ij} = \langle \alpha_i, \alpha_j \rangle = (\alpha_i, \alpha_j^\vee)$.

Then Matsumoto's Lemmas~5.2 and 5.4 assert that:
\[ {}^{h_\alpha(t)}\!x_\beta(u) = x_\beta(t^{\langle \beta,  \alpha \rangle}u)\]
\[ {}^{h_\alpha(t)}\!h_\beta(u) = h_\beta(t^{\langle \beta, \alpha \rangle} \cdot u) \cdot h_\beta(t^{\langle \beta,  \alpha \rangle})^{-1}. \]
\[[h_\alpha(s), h_\beta(t)] = \{s, t^{\langle \alpha, \beta \rangle}\}_\alpha = \{t, s^{\langle \beta, \alpha \rangle}\}_\beta^{-1}\]

Definition of Steinberg symbol is:
\[ \{ s, t \}_\alpha = h_\alpha(s) \cdot h_\alpha(t) \cdot h_\alpha(st)^{-1} \]

Recall the definition of the Dennis--Stein symbol (cf. III.5.11 within Weibel's book)
\[ \langle r,s \rangle _ \alpha = x_{-\alpha}\left(-\frac{s}{1 - rs}\right) \cdot x_{\alpha}(-r) \cdot x_{-\alpha}(s) \cdot x_{\alpha}\left(\frac{r}{1-rs}\right) \cdot h_{\alpha}(1 - rs)^{-1}. \]

Statement \[x_{\alpha}(aX^{-1}) x_{-\alpha}(mX) x_{\alpha}(-a(1+am)^{-1}X^{-1}) \cdot \{X, 1+am\} \in G_+.\]

$y := x_{\alpha}(aX^{-1}) x_{-\alpha}(mX) x_{\alpha}(-a(1+am)^{-1}X^{-1})$,

@@

Using $\pi(z) = 1$ we get 
\begin{multline}z = z^{h_{ik}^{-1}(X)} = \\ x_{ji}(-m(1+am)^{-1}) x_{ij}(a) x_{ji}(m) \cdot x_{ij}(-a(1+am)^{-1})\{X, (1+am)^{-1}\} \cdot h_{ij}((1+am)^{-1}) \in G. \end{multline}
